---
title: "Analysis of effect of advertising on the sales"
output: html_notebook
---
## *I. Simple linear regression:*

In simple linear regression, there is only one independent variable x and the relationship between the dependent variable y and x is modeled as straight line:
<br/>
&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp; 𝑦= $\alpha$ + ${\beta x}$

$\beta$ is the slope of the line and $\alpha$ is the intercept. Together, $\alpha$ and $\beta$ are known as the model coefficients or parameters.Once we have used training data to produce estimates $\hat{\alpha}$ and $\hat{\beta}$ for the model coefficients, we can predict future values of y by using the following equation:
<br/>
&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp; $\hat{y}$ = $\hat{\alpha}$ + $\hat{\beta} x$

Where $\hat{y}$ is the predicted value (it could differ from the actual value y)

Let $\hat{y_{i}}$ = $\hat{\alpha}$ + $\hat{\beta} x_{i}$ be the prediction for y based on the ith value of x.
<br/>
Then $e_{i}$ = $y_{i}$ − $\hat{y_{i}}$ represents the ith residual — this is the difference between the ith observed value and the ith value that is predicted by our linear model. In a sense, it measures the error of prediction for the ith value. 

<br/>
We define the residual sum of squares (RSS) as:
<br/>
&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp; RSS = $\sum {(y_{i} − \hat{y_{i}})^2}$  = $\sum e_{i}^2$

The Ordinary Least Squares (OLS) method determines 􀷜$\hat{\alpha}$ and $\hat{\beta}$ so that to minimize RSS. It is mathematically proved that RSS is minimized for the following values of $\hat{\alpha}$ and $\hat{\beta}$:
$\hat{\beta} = \sum (x_{i} - \overline{x})(y_{i} - \overline{y})/\sum (x_{i} - \overline{x})^2$

<br/>
$\hat{\alpha} = \overline{y} − \hat{\beta} \overline{x}$


## *II. Applying Simple linear regression to predict sales:*

### **Data Exploration:**
<br/>
**1. Reading Advertising data from the file into a data frame:**
```{R}
advertising = read.csv("Advertising.csv")
```

<br/>  
**2. 
<br/>
    i. Structure of the dataset:**
```{R}
str(advertising)
```
The dataset contains 200 observations and four variables: the money that is spent on TV, newspaper, or radio ads and the sales in thousand dollars. **We want to study the relationship between sales and TV ads.**

<br/>  
**3. 
<br/>
    i. Scatterplot to analyse correlation between TV ads and sales:**
```{r message=FALSE, warning=FALSE}
attach(advertising)
```
    
```{R}
plot(sales ~ TV, col = "#22B3C8", ylab = "Sales", xlab = "TV", main = "Sales vs TV ads", cex.lab = 0.8, cex.main = 0.9)
```
From the scatterplot we can say there exists a positive correlation between sales and TV ads.
<br/>
    ii. Analyse correlation between TV ads and sales using cor function:**
```{r}
cor(TV, sales)
```
cor function shows there is a strong enough positive correlation between TV and sales.
   
<br/>  
**4. Using lm() function to fit a linear regression model to the data:**
```{r}
advertising_lm = lm(sales ~ TV, data = advertising)
coefficients(advertising_lm)
```
In other words $\hat{\alpha}$ = 7.03259355 and $\hat{\beta}$ = 0.04753664
   
<br/>  
**5. Using coefficients from linear regression model to draw a line through the scatterplot:**
```{r}
plot(sales ~ TV, col = "#22B3C8", ylab = "Sales", xlab = "TV", main = "Sales vs TV ads", cex.lab = 0.8, cex.main = 0.9)
abline( 7.03259355,0.04753664,col="deeppink4" )
```
The coefficients of this line drawn through the scatterplot is chosen such that RSS is minimum.

